---
title: "Simple document"
author: Tong Su
date: 2024-091-0
output: github_document

      
---
#output: html_document:toc: true toc_float: true code_folding: hide
#output:word_document#
#output:Github_document#
      
I'm an R Markdown document! 

```{r,echo=FALSE, message=FALSE}
library(tidyverse)
```
I loaded necessary packages, (e.g.tidyverse)
# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3 learning assessment 
This is code for the learning assessment at P8105_0910

```{r leanring_assessment_1, message=FALSE}
df = 
  tibble(
  norm_samp = rnorm(n = 500,mean = 1),
  log_norm_samp = norm_samp>0,
  abs_norm_samp = abs(norm_samp)
  )
ggplot(df, aes(x = abs_norm_samp)) + geom_histogram()
median_samp = median(pull(df, norm_samp))
```
Here's code to creat a histogram.
```{r, eval=FALSE, echo=FALSE}
ggplot(df, aes(x = abs_norm_samp)) + geom_histogram()
median_samp = median(pull(df, norm_samp))
```

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell